\chapter*{Abstract}
\thispagestyle{empty}
\addtocounter{page}{-1}

This paper aims to present an efficient way to make photographs easier to find by similarity and easy to recommend to users. The main problem of creating such a system is how photographs should be transformed such that mathematical operations can be applied on them.

Recommender system have been among us for quite a few years now. They have become so important that no major content aggregator website functions without one. Online marketplaces use them as a way to advertise in order to tailor to the user's needs. Search engines find relevant information and return the source where they were found.

Pictures have now become a very important in our day-to-day communication. An internet user has become accustomed to them being one of the primary sources of information. While text information has become easier to find, that cannot be said about photographic content.

Our approach tries to recommend similar pictures based on the identified objects in them and processes them into vectors using word embeddings. In order to create a well-defined space, a word embedding operation acts as a fuzzy membership function with multiple values being used to provide a multi-dimensional point. The obtained points are fed into a nearest neighbours data structure for fast querying.

This thesis is structured into 8 chapters, with the first 4 focusing on the background theory. First, general aspects of the domain of machine learning are presented, followed by all the other theoretical aspects used in the full system: object detection with neural networks, word embeddings and clustering. Following these comes the approach, structured in two chapters, one focusing on providing an in-detail solution and the second on evaluating the solution. The next chapter provides the user with a user manual and the last one focuses on drawing a conclusion and pondering on future work.

This work is the result of my own activity. I have neither given nor received unauthorised assistance on this work.

\begin{flushright}
Tudor V\u{a}ran
\end{flushright}