\chapter*{Introduction}
\addcontentsline{toc}{chapter}{\textbf{Introduction}}
\markright{INTRODUCTION}

As the need for more data increases it is becoming increasingly hard to access relevant one. The internet is now an endless network full of websites with content which are not always available to everyone. Usually, the user most know exactly what to look for and that website must offer them the content which meets the exact criteria.

However, an increasing demand for a product does not mean there is a supply available. There must be a middle ground, where the demander adjust their needs and the supplier attempts to provide the other part interesting products.

Recommender systems are now widely used on the internet. Every major website uses one in order to keep the user engaged. Internet giants like Facebook, Amazon and Google have integrated one at least once in their services. Perhaps the biggest example of a recommender system the Google search engine, which is a great attempt performing a meeting halfway between demand and supply. It has now become the default way to search information on the internet.

A new area of research in these types of system are photographs. It peaks the interest of businesses because they are widely used as a way of communication on the internet, no matter if they are vacation pictures, informative or even memes. There is a saying that a \textit{picture is worth a thousand words}. But like all information, not finding it can be frustrating.

This paper aims to investigate the use of recommender systems in recommending similar pictures to users based on the objects found in them. The paper is structured in 8 chapters, as follows:

\begin{itemize}
\item{Chapter \ref{chap:ml}, Machine Learning, presents general aspects of this large domain of Artificial Intelligence.}
\item{Chapter \ref{chap:obj}, Object Detection, focuses on the theory behind identification of objects in pictures using neural networks.}
\item{Chapter \ref{chap:words}, Word Embedding, provides useful information on how words can be transformed into mathematical objects which allow operations on them.}
\item{Chapter \ref{chap:cluster}, Clustering, delves into the most important aspect of recommender systems, data querying.}
\item{Chapter \ref{chap:approach}, Our Approach, defines the problem and formalises a possible solution to it.}
\item{Chapter \ref{chap:results}, Results and evaluation, discusses the progress made and asses the quality of the system.}
\item{Chapter \ref{chap:app}, Application, showcases an application in the form of a simple website which implements the solution. It also contains an installation guide and user manual.}
\item{Chapter \ref{chap:conclusion}, Conclusions, acts as summariser for the paper, mentioning what has been done and what can be improved.}
\end{itemize}